Flexible Scientific Data Management for Plant Phenomics Research

### 2013-04-15 s4biodiv2013/Rebuttals.txt

The manuscript also feels like it was written by someone extremely familiar with the system, as it uses phraseology that likely only has meaning to them.  For example "External ontologies must currently be mapped into the PODD system to define the expected status of the classes and properties with respect to the basic PODD concepts" - I have read that sentence multiple times and still cannot decypher what it means to "define the expected status of the classes and properties", or what the authors mean by "mapping" external ontologies "into" the PODD system.  Other examples of this include:

"allow scientists to generate datasets before they were certain about the semantic meaning of their work" - what does that mean?

 *****

 Rebuttal : Rewrote Section 5 Paragraph 2 to include an example of mapping the Crop Ontology into PODD. Rewrote Section 2.2 Paragraph 1 to clarify that scientists are able to sparsely populate PODD projects with links to community defined upper ontologies.

@@

 *****

Most of the paragraph beginning "The basic PODD project...", with statements like "annotate images of a plant with a trait in only one case, without annotating other images" and "these horizontal links are not constrained by the basic scientific project structure" (what horizontal links are you referring to, and what are "horizontal links"?)

 *****

 Rebuttal : Rewrote Section 2.2 Paragraph 2 to remove reference to horizontal links. The sparse linking explanation is given in Section 2.2 Paragraph 1.

### 2013-04-15 s4biodiv2013/PODD-S4BIODIV-Submission.tex
address comments for Section 2.2

\subsection{Redesign of the Phenomics Ontology Driven Data repository}
The PODD repository relies on semantic web technologies to
manage phenomics data and metadata. Although both ontologies and mappings are
essential, in PODD it was necessary to build the system with a relaxed
ontological vocabulary. This enables scientists to sparsely populate their datasets 
and sparsely link to community defined upper ontologies as necessary. This 
allows scientists to continue to maintain projects containing curated
scientific concepts alongside raw experimental data. The PODD repository was 
redesigned based on an evaluation of the original software \cite{Li2010} that 
found it was not able to scale sufficiently to suit the HRPPC needs due to design 
and implementation deficiencies. The major differences to the software implemented 
by \cite{Li2010} are that projects are no longer the only supported top object type, 
and projects are not stored in multiple parts, as that approach was not able to 
scale as was originally hypothesised.

In the case of PlantScan\textsuperscript{\texttrademark} a PODD project contains top level branches describing the 
various parts of a scientific project. These include a branch for raw data, along with separate
branches for results, analysis, and publications related to the project. In the
case of raw data, the semantics are not necessarily clear and are not easily defined by the
automated platforms collecting the data. 
% Scientists are able to sparsely attach meaning
% using horizontal links between different branches, using the OWL Open World
% Assumption to allow extra semantic annotations to be attached in future. 
The scientist may then semantically link the data with results, conclusions, and external ontologies.
For example, a scientist may annotate the data objects representing images of a plant with a trait 
that is defined in an external community ontology. They may also annotate the image with a link 
to a trait that is defined inside of the project, particularly in cases where the trait is novel 
and not represented in a community ontology.
%These horizontal links are not constrained by
%the basic scientific project structure, so they are able to entail novel
%meanings independent of the ontology, including untested hypotheses, process
%annotations and meaningful scientific results.

>>>>

\subsection{Redesign of the Phenomics Ontology Driven Data repository}
The PODD repository relies on semantic web technologies to
manage phenomics data and metadata. Although both ontologies and mappings are
essential, in PODD it was necessary to build the system with a relaxed
ontological vocabulary. This enables scientists to sparsely populate their datasets 
and sparsely link to community defined upper ontologies as necessary. This 
allows scientists to continue to maintain projects containing curated
scientific concepts alongside raw experimental data. The PODD repository was 
redesigned based on an evaluation of the original software \cite{Li2010} that 
found it was not able to scale sufficiently to suit the HRPPC needs due to design 
and implementation deficiencies. The major design differences to the software implemented 
by \cite{Li2010} are that projects are no longer the only supported top object type, 
and projects are not stored in multiple parts, as that approach was not able to 
scale as was originally hypothesised.

A PODD project in PlantScan\textsuperscript{\texttrademark} contains top level branches describing the 
various parts of a scientific project. These include a branch for raw data, along with separate
branches for results, analysis, and publications related to the project. In the
case of raw data, the semantics are not necessarily clear and are not easily defined by the
automated platforms collecting the data. 
% Scientists are able to sparsely attach meaning
% using horizontal links between different branches, using the OWL Open World
% Assumption to allow extra semantic annotations to be attached in future. 
The scientist may later semantically link the data with results, conclusions, and external ontologies.
For example, a scientist may annotate the data objects representing images of a plant with a link to a trait 
that is defined in the Plant Ontology. They may also annotate the image with a link 
to a trait that is defined inside of the project, such as when the trait is novel 
and not represented in a community ontology.
%These horizontal links are not constrained by
%the basic scientific project structure, so they are able to entail novel
%meanings independent of the ontology, including untested hypotheses, process
%annotations and meaningful scientific results.
